### 2017-12-11 readme.rmd
word smithing

## Using sensitivity to understand the support landscape

@@

Feuda *et al.* explain why they interpret the sensitivity they and others present as support for Porifera-sister in a few passages, including:

@@

One of the most critical steps to take is to change the way we talk about the problem. In particular, insignificant phylogenetic results should not be presented as definitive resolutions of tough problems. This should always apply, but especially so in the case of highly contested questions of such broad interest. Making strong statements about insignificant results gives the impression that phylogenetic methods are broken as a question seems to bounce from one extreme answer to the other. They are not. How we talk about phylogenies is broken.

>>>>

## Sensitivity and the support landscape

@@

Feuda *et al.* explain why they interpret their results as evidence for Porifera-sister, even though support is sensitive to multiple factors, as follows:

@@

One of the most critical steps to take is to change the way we talk about the problem. In particular, non-significant phylogenetic results should not be presented as definitive resolutions of tough problems. This should always apply, but especially so in the case of highly contested questions of such broad interest. Making strong statements about non-significant results gives the impression that phylogenetic methods are broken as a question seems to bounce from one extreme answer to the other. They are not. How we talk about phylogenies is broken.
